Describing vocalizations in young children: A big data approach through citizen science annotation

### 2021-01-28 202010_jslhr/paper.Rmd
nearly done with new pipeline

printr=function(x) sub("0.", ".", round(x,3))
```

```{r read-in}
# read datasets

data_ang <- read.csv("segment_AS.csv",header=T,sep =",")
data_td <- read.csv("segment_LRC.csv")
data_all<-rbind(data_ang, data_td)

>>>>

printr=function(x) sub("0.", ".", round(x,3))

#document session info

sink("lastknit_session_info.txt")
sessionInfo()
sink()
```

```{r read-in}

# read datasets
data_ang <- read.csv("segment_AS.csv",header=T,sep =",")
data_td <- read.csv("segment_LRC.csv")
data_all<-rbind(data_ang, data_td)
